---
title: "Using the perfi package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using the perfi package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Loading bank transaction sheets

The `perfi` package provides a suite of tools for importing, cleaning, analyzing, and visualizing personal finance transaction data from different banks. First, we load the `perfi` package.

```{r setup}
library(perfi)
```

Then, depending on your bank, use `read_boa()` or `read_USBank()` to import your transaction sheet. To load our example data stored in `perfi`, we first use `read_example()`. Below is an example of importing a BOA transaction sheet.

```{r}
example <- read_example("boa_example_data.csv")
user_data <- read_boa(example)
```

User can also import transaction sheets from the US Bank.

```{r}
example_usb <- read_example("usbs_example_data.csv")
user_usb_data <- read_USBank(example_usb)
```


## Summary stats

Once we have the data loaded, we can use the `summary_stats()` function to calculate user's total expenditure and deposits in the given period.

```{r}
summary_stats(user_data)
```


## Spending by category

A more detailed report of user's expenditure can be created with the `avg_spend()` function, in which a bar plot of expenditure will be created. Each bar represents the user's expenditure of the week, accompanied with a dotted line indicating their average weekly spending.

```{r}
avg_spend(user_data)
```


## Calculating budget allocation

To determine the portion of their income allocated to needs, wants, and savings, user input their income to `budget_income()` function. The default distribution of needs, wants, and savings is 50%, 30%, and 20%, respectively. The default frequency is bi-weekly.

```{r}
budget_income(1000)
```
User can alter their preferences with `needs_percent`, `wants_percent`, `savings_percent`, and `freq` arguments. The function always returns bi-weekly budget.

```{r}
budget_income(1000, needs_percent = 0.4, wants_percent = 0.3, savings_percent = 0.3, freq = "weekly")
```


## Expenditure by category

The `perfi` package also enables users to visualize their expenditure by category. Users can generate a pie chart of this kind using the `generate_pie()` function.

```{r}
generate_pie(user_data)
```

